Lifting CDCL to Relational Domains

### 2016-10-13 domains.tex

One of the requirements for a clause learning SAT solver 
is that each element of the partial assignments domain 
needs to have a decomposition into precisely complementable 
elements.  This property of the underlying domain helps to 
guide the search away from the conflicting region of the 
search space.
\rmcmt{define precise complement}
Thus, clause learning SAT solvers requires a weak complementation property
of the abstraction.  However, numerical abstract domain,  such as 
intervals and octagons are intersections of complementable half-spaces. 
The commonly used library for numerical abstract domains  
is the APRON C library~\cite{apron}.  This library is 
used for the static analysis of the numerical variables 
of a program by abstract interpretation. APRON provides a 
C API interface to various abstract domains and libraries 
such as {\em BOX}, {\em OCTAGON}, {\em Convex Polyhedra} and
{\em Linear Equalities} library.  The aim of such analysis is 
to compute invariants over numerical variables in the 
program~\cite{se2011}.

APRON library is specialized for the abstract interpretation 
framework which does not require complementation property.  
To this end, we implement our own template-based 
interval, octagon and equality domains which supports 
complementation operator.  
%For example, the octagon in Figure~\ref{octagon} can be written as a conjunction of:
%\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2)
%\land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
\pscmt{That's no valid motivation. We never complement a whole octagon, but just a
  meet-irreducible. It's trivial to do that with APRON. The reason was
a different one: APRON does not support all C operators, e.g. the bitwise operators.}
For example, the complementation of the octagon in Figure~\ref{octagon} can be written as disjunction of:
\[(x<-2) \lor (x>1) \lor (y<-1) \lor (y>2) \lor (x+y>2) \lor (x-y>1) \lor (y-x>3) \lor (-x-y>2)\]

>>>>

\subsection{Properties of Domain Elements for Decision and Learning}
An important property for a clause learning SAT solver 
is that each element of the partial assignments domain 
are decomposable into precisely complementable 
elements.  This property of the domain helps to 
guide the search away from the conflicting region of the 
search space.  
\rmcmt{define precise complement}
Thus, clause learning SAT solvers requires a weak complementation property
of the abstraction.  Most numerical abstract domain, such as intervals, 
octagons, polyhedra have complementation property, that is, the domain 
elements are intersections of complementable half-spaces. 
\Omit {
The commonly used library for numerical abstract domains  
is the APRON C library~\cite{apron}.  This library is 
used for the static analysis of the numerical variables 
of a program by abstract interpretation. APRON provides a 
C API interface to various abstract domains and libraries 
such as {\em BOX}, {\em OCTAGON}, {\em Convex Polyhedra} and
{\em Linear Equalities} library.  The aim of such analysis is 
to compute invariants over numerical variables in the 
program~\cite{se2011}. 
}
Abstract Domain library, such as APRON C library~\cite{apron}, 
is specialized for the abstract interpretation framework which 
does not require complementation property.  To this end, we 
implement our own template-based polyhedra domain and interval 
domain which supports complementation operator.  
%For example, the octagon in Figure~\ref{octagon} can be written as a conjunction of:
%\[(x>=-2) \land (x<=1) \land (y>=-1) \land (y<=2) \land (x+y<=2)
%\land (x-y<=1) \land (y-x<=3) \land (-x-y<=2)\] 
\pscmt{That's no valid motivation. We never complement a whole octagon, but just a
  meet-irreducible. It's trivial to do that with APRON. The reason was
a different one: APRON does not support all C operators, e.g. the bitwise operators.}
For example, the complementation of the octagon in Figure~\ref{octagon} can be written as disjunction of:
\[(x<-2) \lor (x>1) \lor (y<-1) \lor (y>2) \lor (x+y>2) \lor (x-y>1) \lor (y-x>3) \lor (-x-y>2)\]
